## Copyright 2018 Kai Puolamaki <kai.puolamaki@aalto.fi>
## Copyright 2018 Aalto University, Espoo, Finland
##
## Permission is hereby granted, free of charge, to any person obtaining
## a copy of this software and associated documentation files (the
## "Software"), to deal in the Software without restriction, including
## without limitation the rights to use, copy, modify, merge, publish,
## distribute, sublicense, and/or sell copies of the Software, and to
## permit persons to whom the Software is furnished to do so, subject to
## the following conditions:
##
## The above copyright notice and this permission notice shall be
## included in all copies or substantial portions of the Software.
##
## THE SOFTWARE IS PROVIDED "AS IS", WITHOUT WARRANTY OF ANY KIND,
## EXPRESS OR IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES OF
## MERCHANTABILITY, FITNESS FOR A PARTICULAR PURPOSE AND
## NONINFRINGEMENT. IN NO EVENT SHALL THE AUTHORS OR COPYRIGHT HOLDERS BE
## LIABLE FOR ANY CLAIM, DAMAGES OR OTHER LIABILITY, WHETHER IN AN ACTION
## OF CONTRACT, TORT OR OTHERWISE, ARISING FROM, OUT OF OR IN CONNECTION
## WITH THE SOFTWARE OR THE USE OR OTHER DEALINGS IN THE SOFTWARE.


---
title: "Runtime experiment"
output: html_notebook
---


```{r}
set.seed(42)

source("tiling.R")

testf <- function(n=101,m=97,k=7,iter=100) {
  cat(sprintf("testf: n = %d m = %d k = %d iter = %d\n",n,m,k,iter))
  data1 <- matrix(rep(1:n,m),n,m)
  data2 <- matrix(rep(1:m,each=n),n,m)
  hits <- 0
  for(i in 1:iter) {
    junk <- tiling(n,m)
    rr <- sample.int(n,size=2)
    data3 <- matrix(0,n,m)
    data3[rr[1],] <- 1
    data3[rr[2],] <- 2
    tiles <- lapply(1:k,function(i) list(R=sample.int(n,size=sample.int(n)),
                                         C=sample.int(m,size=sample.int(m))))
    tiles <- lapply(tiles,
                    function(x) list(R=if(length(intersect(x$R,rr))>0) union(x$R,rr) else x$R,
                                     C=x$C))
    for(tile in tiles) {
      junk$addtile(tile$R,tile$C)
    }
    pdata <- junk$permutedata(data1)
    for(tile in tiles) {
      slice <- pdata[tile$R,tile$C,drop=FALSE]
      if(!setequal(tile$R,slice[,1]) || any(apply(slice,1,function(x) any(x!=x[1])))) stop("error: permutation violates a tile constraint.")
    }
    pdata <- junk$permutedata(data2)
    if(any(apply(pdata,2,function(x) any(x!=x[1])))) stop("error: permutation doesn't stay within column.")
    pdata <- junk$permutedata(data3)
    if(pdata[rr[1],1]!=1 || pdata[rr[2],1]!=2) hits <- hits+1
  }
  if(hits==0) stop("error: suspiciusly few swaps.")
  cat("success\n")
}

runtime <- function(n=101,m=97,k=7) {
  tiles <- lapply(1:k,function(i) list(R=sample.int(n,size=floor(n/10)),
                                       C=sample.int(m,size=floor(m/10))))
  tinit <- system.time( junk <- tiling(n,m) )["elapsed"]
  tmaxadd <- -Inf
  for(tile in tiles) {
    R <- tile$R
    C <- tile$C
    tmaxadd <- max(tmaxadd,system.time( junk$addtile(R,C) )["elapsed"])
  }
  data <- matrix(1:(n*m),nrow=n,ncol=m)
  tpermute <- system.time( pdata <- junk$permutedata(data) )["elapsed"]
  list(tinit=tinit,tmaxadd=tmaxadd,tpermute=tpermute)
}
```


```{r}
version

testf()

cat("$n$ & $m$ & $k$ & $t_{init}$ & $t_{permute}$ & $t_{max,add}$ \\\\\n")
for(n in c(5000,10000)) {
  for(m in c(50,100)) {
    for(k in c(25,50,100)) {
      a <- runtime(n,m,k)
      cat(sprintf("$%5d$ & $%3d$ & $%3d$ & $%.2f$ & $%.2f$ & $%.2f$ \\\\\n",n,m,k,a$tinit,a$tpermute,a$tmaxadd))
    }
  }
}

```
